---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r}

#rm(list=ls())  # clear all variables in current environment
#graphics.off() # clear all plots

```

# Introduction

This README presents the answers for the Financial Econometrics Paper 2021. The paper consisted of 6 questions. Below, approaches to answering the questions as well as key plots and functions will be presented. 

#Question 1 

This question was interesting because it tapped into key concepts in finance. Yield spreads are financial indicators that tell investors the likelihood of a recession or a recovery in a market. To calculate a yield spread, one can take any longer-term dated bond yield and subtract the shorter term dated bond yield. When analyzing yield spreads, the investor observes the yield spreads and can see if an economy is heading for recession or recovery. When spreads increase, this signifies an increase in risky bond securities being offered to the market to compensate for risks in an economy. As spreads decrease, this usually indicates that an economy is in recovery and fewer rates.


The first thing to do was to load all my packages and data necessary. These included the following code:

```{r, include=FALSE}

pacman::p_load("tidyr", "tbl2xts","devtools","lubridate", "readr", "PerformanceAnalytics", "ggplot2", "dplyr","tidyverse","xts")

bonds_2y<-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/bonds_2y.rds", refhook = NULL)

bonds_10y <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/bonds_10y.rds", refhook = NULL)

SA_bonds <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/SA_bonds.rds", refhook = NULL)   

BE_Infl <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/BE_Infl.rds", refhook = NULL)   

usdzar <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/usdzar.rds", refhook = NULL) 

ZA_Infl <- readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/ZA_Infl.rds", refhook = NULL) 

IV <- readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/IV.rds", refhook = NULL) 
   
```

After this was done, I observed the data by making use of ggplot where I tried to look at the bond yields and called the graph "g". The code is below:


```{r,  include=FALSE}
g <- ggplot(data = SA_bonds, aes(x =  date)) +
  geom_line(aes(y = ZA_10Yr, colour = "10 Year")) +
  geom_line(aes(y = ZA_2Yr, colour = "2 Year")) +
  geom_line(aes(y = SA_3M, colour = "3 month")) +
      theme_minimal() +
  scale_colour_manual("", 
                      values = c("2 Year"="green", "10 Year"="red", 
                                 "3 month"="blue")) +
  xlab(" ") +
  scale_y_continuous("Bond Yields ", limits = c(-5,20)) + 
  labs(title="SA Bond Yields")
```

```{r}
g
```


Next I showed the USD/ZAR