---
title: "Question 6"
author: '20903936'
date: "12/5/2021"
output:
  pdf_document: default
  html_document: default
---

```{r, include=FALSE}

pacman::p_load("tidyr", "tbl2xts","devtools","lubridate", "readr", "PerformanceAnalytics", "ggplot2", "dplyr","tidyverse","xts","timeSeries","fPortfolio","quantmod")

MAA<-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/MAA.rds", refhook = NULL) %>% select(date,Ticker,Price)

msci <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/msci.rds", refhook = NULL)
```


```{r}

# this was not working
#msci<- msci%>% filter(Name %in% c("MSCI_ACWI", "MSCI_USA", "MSCI_RE", "MSCI_Jap"))
```

#Introducition

This section is above portfolio construction. Here we had to build a balanced fund using the following criteria: 

- Long-only strategy
- When using covariance and mean forecasts, use a look-back of less than 3 years;
- Do not hold any assets with less than 3 years’ returns data;
- Apply Quarterly Re balancing;
- Limit exposure to Bonds and credit instruments at 25%;
- Limit exposure to Equities at 60%;
- Limit single asset exposure at 40


```{r}

#use the esquisse::esquisser(msci) visualise.

library(ggplot2)

ggplot(msci) +
 aes(x = date, y = Price, colour = Name) +
 geom_line(size = 0.5) +
 scale_color_hue(direction = 1) +
 labs(x = "Year", y = "Returns", title = "MSCI indexes", subtitle = "MSCI Return series") +
 theme_minimal()


```


```{r}
#use the esquisse::esquisser(MAA) visualise.

library(ggplot2)

ggplot(MAA) +
 aes(x = date, y = Price, colour = Ticker) +
 geom_line(size = 0.5) +
 scale_color_hue(direction = 1) +
 labs(x = "Year", y = "Price", title = "Global Indexes", caption = "Plot of Global Indexes") +
 theme_minimal()

```

Lets combine these data sets and try some portfolio construction

```{r}

#colnames(msci)[2] <- "Ticker"

#dataset <- rbind(MAA, msci)


```


