---
title: "Question 5"
author: '20903936'
date: "12/5/2021"
output:
  pdf_document: default
  html_document: default
---

```{r}
pacman::p_load("tidyr", "tbl2xts","devtools","lubridate", "readr", "PerformanceAnalytics", "ggplot2", "dplyr","tidyverse","xts")

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

msci <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/msci.rds", refhook = NULL)


bonds_10yr <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/bonds_10y.rds", refhook = NULL)

comms <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/comms.rds", refhook = NULL)

bonds_2yr <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/bonds_2y.rds", refhook = NULL)

```

# Introduction

My task in this report is to use the MSCI total return profiles as well as bond and comodity return profiles to show that these returns are converging.

The graph below shows the MCSI indexes plot or returns.

```{r, include=FALSE}
library(ggplot2)

g100 <- ggplot(msci) +
 aes(x = date, y = Price, colour = Name) +
 geom_line(size = 0.5) +
 scale_color_hue(direction = 1) +
 labs(x = "Year", y = "Returns", title = "MCSI Index Plot", caption = "MCSI indexes plot of returns") +
 theme_minimal()
```


```{r}
g100
```

THe plot shows that there are a variety of indexes in the dataset. It may be necessary to only select those variables that are country or region specific to create a reasonable comparisons between returns across asset classes.

```{r, include=FALSE}

g200<-ggplot(comms) +
 aes(x = date, y = Price, colour = Name) +
 geom_line(size = 0.5) +
 scale_color_hue(direction = 1) +
 labs(x = "Year", y = "Return", title = "Commodities Returns", subtitle = "Showing commodity prices") +
 theme_minimal()
```


```{r}
g200
```
The above plot shows the 
 

```{r, include=FALSE}

g300 <- bonds_10yr %>% filter(Name == "CHINA_10Yr") %>% ggplot() +
 aes(x = date, y = Bond_10Yr, colour = Name) +
 geom_line(size = 0.5) +
 scale_color_hue(direction = 1) +
 labs(x = "Year", y = "Yields", title = "10 Year bond Yields", subtitle = "Showing all the 10 Year", 
 caption = "Showing all the data in the data set") +
 theme_minimal()
```


To illustrate the above tasks. I will use use Chinesse assets to show 

```{r}
g300

```


```{r, include=FALSE}
# China msci return 

China_ret <- msci %>% filter(Name=="MSCI China") %>% arrange(date) %>% mutate(china_msci_ret = Price/lag(Price) - 1)


g400 <- China_ret %>% ggplot() +
 aes(x = date, y = china_msci_ret, colour = Name) +
 geom_line(size = 0.5) +
 scale_color_hue(direction = 1) +
 labs(x = "Year", y = "Return", title = "MSCI China Return", subtitle = "Showing all the 10 Year", 
 caption = "Showing all the data in the data set") +
 theme_minimal()
```


```{r}
g400
```


```{r, include=FALSE}
#bcom returns

Gold_ret <- comms %>% filter(Name=="Gold")%>% arrange(date) %>% mutate(gold_ret = Price/lag(Price) - 1)


g4<- Gold_ret  %>% ggplot() +
 aes(x = date, y = gold_ret, colour = Name) +
 geom_line(size = 0.5) +
 scale_color_hue(direction = 1) +
 labs(x = "Year", y = "Price", title = "Gold Returns", subtitle = "Showing all the 10 Year", 
 caption = "Showing all the data in the data set") +
 theme_minimal()
```


```{r}
g4

```

From the above charts there seems to be some convergence in returns. This is a very interesting result as it may mean that investors a gradually moving into cash or even cryptocurrencies. 


