---
title: "README"
author: '20903936'
date: "12/4/2021"
output:
  pdf_document: default
  html_document: default
---

Question 3:

In this brief report, I aim to show the JSE the concentration and commonality of returns within the Top 40 index (J200). In order to do so, I will look at using Principal Component Analysis and rolling constituent correlation perspective to illustrate. In my answer I will use stratification of monthly volatility by calculating the J200 index returns and comparing return source concentrations for periods of high volatility only. 

```{r}

# Importing the data
T40 <-readRDS("/Users/mathlogonolomashitisho/Desktop/Economics Masters /Semester 2/Fin Metrics/Financial Econometrics Practical/data/T40.rds", refhook = NULL)
```


Let begin by stratifying the returns for times during high volatility. 

```{r}
library(rmsfuns)
pacman::p_load("tidyr", "tbl2xts","devtools","lubridate", "readr", "PerformanceAnalytics", "ggplot2", "dplyr")

```



```{r}
#Here , there is no need to consider before 2008 because the data has already provided for the surviving tickers. Also changed NA to zero because sometimes a a ticker will not make it into the index.

T40 <- T40 %>% group_by(date) %>% dplyr::mutate(Return= coalesce(Return,0)) %>% dplyr::mutate(J200= coalesce(J200,0)) %>% mutate(J200return = J200 * Return) %>% select(-J400)
```


```{r}
T40 <-
  
  T40 %>% group_by(Tickers) %>% 
  
  mutate(Top = quantile(J200return, 0.99), Bot = quantile(J200return, 0.01)) %>% 
  
  mutate(Return = ifelse(J200return> Top, Top, 
                         
                         ifelse(J200return < Bot, Bot, J200return))) %>% ungroup() %>%  mutate(YearMonth = format(date, "%Y%B"))


```


```{r}
T40SD <-T40  %>% 
  
  mutate(YearMonth = format(date, "%Y%B")) %>% 
  
  group_by(YearMonth) %>% summarise(SD = sd(J200return)*sqrt(52)) %>% 
  
  # Top Decile Quantile overall (highly volatile month for ZAR:
  mutate(TopQtile = quantile(SD, 0.8),
         
         BotQtile = quantile(SD, 0.2))
```


```{r}
Hi_Vol <- T40SD %>% filter(SD > TopQtile) %>% pull(YearMonth)

Low_Vol <- T40SD %>% filter(SD < BotQtile) %>% pull(YearMonth)
```

```{r}
# Create generic function to compare performance:

Perf_comparisons <- function(Idxs, YMs, Alias){
  # For stepping through uncomment:
  YMs <- Hi_Vol
  
  Unconditional_SD <- 
    
  Idxs %>% 
    
    group_by(Tickers) %>% 
    
    mutate(Full_SD = sd(Return) * sqrt(252)) %>% 
    
    filter(YearMonth %in% YMs) %>% 
    
    summarise(SD = sd(Return) * sqrt(252), across(.cols = starts_with("Full"), .fns = max)) %>% 
    
    arrange(desc(SD)) %>% mutate(Period = Alias) %>% 
    
    group_by(Tickers) %>% 
    
    mutate(Ratio = SD / Full_SD)
    
    Unconditional_SD
  
}
```


```{r}
#Extract the Tickers with monthly high volatility

perf_hi <- Perf_comparisons(T40, YMs = Hi_Vol, Alias = "High_Vol")

perf_lo <- Perf_comparisons(T40, YMs = Low_Vol, Alias = "Low_Vol")

```

PCA Analysis:


```{r}
#Removing rows with missing values 

perf_hi <-na.omit(perf_hi)

```


Mean centering J200returns 
```{r}

T40_Centered <-T40 %>% group_by(Tickers) %>% mutate(J200return_centered = J200return  - 
    mean(J200return)) %>% ungroup()
```


Here we are only interested in Hi volatility periods as stratified above.

```{r}

pacman::p_load(fEcofin)

# prcomp requires wide, numeric data:

data_wide <- T40_Centered %>% filter(T40_Centered$Tickers %in% perf_hi$Tickers) %>% dplyr::mutate(Return= coalesce(Return,0))  %>% select(date, Tickers, J200return_centered) %>% spread(Tickers, 
    J200return_centered) %>% select(-date)


# make sure to account for only those in portfolio
temp<-data_wide[, colSums(is.na(data_wide)) != nrow(data_wide)]

data_wide <- temp %>%
    mutate(
        across(everything(), replace_na, 0)
    )

pca <- prcomp(data_wide)
# We have already cebtered our data, but we could also use
# these built in measures: prcomp(data_wide, center = TRUE,
# scale. = TRUE)

```


```{r}

plot(pca, type = "l")
```


```{r}
summary(pca)
```
AS can be seen in the skree plot above, the elbow of the plot is at 2. This means that there are 2 componants in the high volatility periods that can explain the sources of returns. 

